### 2023-08-30 manuscript.tex
Re-wrote merging HSPs into hits section to address reviewer comments

\subsection{Merging of HSPs into hits}
HSPs were merged in two stages where the first combined non-overlapping HSPs, and the second combined the remaining HSPs. In the first stage, proceeding from highest to lowest bit score, HSPs were marked as ``disjoint'' if they did not overlap with any other HSP previously marked as disjoint. Although this greedy strategy did not necessarily yield the highest-scoring set of disjoint HSPs, it prioritized higher scoring HSPs. In the second stage, all disjoint HSPs were marked as ``compatible,'' and proceeding from highest to lowest bit score the remaining HSPs were marked as compatible if the overlap with any other compatible HSP was no more than 50\% of the length of either. The best hit for each query was chosen as the hit with the highest sum of bit scores from disjoint HSPs. The best hits were filtered by overlap and reciprocity criteria. The overlap criterion was applied first and required that 50\% of residues in the query were aligned in compatible HSPs. This excluded false positives from conserved domains embedded in larger non-homologous proteins by ensuring the hits spanned a sufficient fraction of the query and target sequences. The reciprocity criterion required each query-target pair had a corresponding hit where the roles were reversed, which ensured there was no ambiguity in which target was the best match for the query.

>>>>

\subsection{Merging of HSPs into hits}
Because BLAST can return multiple potentially overlapping HSPs for a query and target sequence pair, HSPs were merged into a single ``hit'' object that encompassed information from HSPs without overlap (``disjoint'') and HSPs with an acceptable amount of overlap (``compatible''). Hits were created by iterating over the HSPs in two passes. In the first pass, proceeding from highest to lowest bit score, HSPs were marked as ``disjoint'' if they did not overlap with any other HSP previously marked as disjoint. Although choosing the highest-scoring subset of HSPs is a kind of ``scheduling problem'' with a known solution, we implemented a simple greedy strategy to prevent fragmentation by prioritizing fewer long and high-scoring HSPs over many short and low-scoring HSPs. In the second pass, all HSPs in the disjoint set were first marked as ``compatible,'' and proceeding from highest to lowest bit score the remaining HSPs were marked as compatible if the overlap with any other compatible HSP was no more than 50\% of the length of either.

The best hit for each query was chosen as the hit with the highest sum of bit scores from only disjoint HSPs. The best hits were filtered by overlap and reciprocity criteria. The overlap criterion was applied first and required that 50\% of residues in the query were aligned in compatible HSPs. This excluded false positives from conserved domains embedded in larger non-homologous proteins by ensuring the hits spanned a sufficient fraction of the query and target sequences. The reciprocity criterion required each query-target pair had a corresponding hit where the roles were reversed, which ensured there was no ambiguity in which target was the best match for the query.
